Background for transient faults in asynchronous circuits

### 2019-11-23 draft_final.tex
final

\begin{document}
\chapter{Introduction}
Digital circuits is the basis of many of present day electronics.  Digital circuits has signals which are represented as discrete values.  This is achieved by choosing a range of voltages that correspond to each discrete value.  Many digital circuits use binary values, that is the signals can only take on the value `logic 0' or `logic 1' (or low/high).  One advantage of only allowing discrete values is that digital circuits are much more robust to noise fluctuations in voltage.  Disregarding the lower level implementation, one can also abstract the function of digital circuits in terms of gates.\\

Although digital circuits are less sensitive to errors due to noise, it can experience other faults in its electronics which ultimately may lead to failure of the component.  Faults may arise due to fabrication defects and radiation such as from space.  Moreover due to new technology and shrinking transistor sizes for MOSFETs, radiation have caused more noticeable effects even at sea level. Thus designing fault free circuits is an important problem to study and solve.  \\  %can still be expanded

This work focuses on a class of digital circuits known as asynchronous circuits.  There is an arbitrary delay on the gates of asynchronous circuits so that each design must be additionally verified to operate correctly under such delays.  There is a variety of uses of asynchronous circuits because it has speedups over synchronous circuits and is also useful for synchronous systems where there is significant clock skew or combining components with different clock cycles and/or interfacing with the real world.  There are some previous work that has been done to make asynchronous circuits fault-tolerant to soft errors.  The design is based on duplicating the circuit and only works for quasi-delay-insensitive circuits which requires a lot of assumptions about how the delays in the underlying transistors function.  The main contributions of this work are that it extends the previous work by proposing a new design.  The new design also follows the duplication strategy but makes fault-tolerant the class of semi-modular speed independent circuits (a class of circuits about the same size as QDI circuits) with looser assumptions on the delay and without significant overhead.  Namely the only assumption is that the combinational logic components are composed of gates and that each gate is allowed to have arbitrary delay, instead of assuming that there is no delay in these components.  Previous designs do not work for this more generalized case of circuits.  This work also proves that such a fault-tolerant model will always work and correct transient faults.  This allows for circuits to be more robust to different types of errors that may occur and prolong the lifetime and types of environments this circuit can be used for.

\section{Synchronous vs Asynchronous circuits}
Digital circuits can be divided into two types, synchronous and asynchronous.  The time it takes for gates to process input signals and then propagate the output to the next gates in a digital circuit may vary widely.  If the timing is somehow off, it is possible for the outputs to be different from the desired value and may cause harm. In synchronous systems this timing variation is dealt with by using a global clock.  The clock is then fed into each flip flop so that the flip flop outputs will lock and update the signals synchronously. The clock cycle frequency is chosen so that all of the gates can finish processing and the correct values are locked for the next cycle. That is, the clock cycle is usually designed to accommodate the slowest logic element. The design of synchronous systems can be complex and is not necessary to understand in detail for this work. \\
\includegraphics[width=\textwidth]{syncex}
\captionof{figure}{Example of a synchronous digital circuit.  Each output is gated by a flip flop that is controlled by the clock}
%possible picture of clock and flip flops?.... redraw as my own

Asynchronous circuits, as the name suggests, do not depend on a clock. As a result there are varying time delays in its components. The goal of designing asynchronous circuits is to make circuits that achieves some specification in spite of the time delays. That is, irrespective of the time delays, the circuit behaves the same way. One main reason that asynchronous circuits are used is that because it does not require clocks to propagate signals, instead as soon as one logic element finishes the signal goes directly to the next element.  This can allow the circuits to have speedups as it is not waiting for the slowest element for each clock cycle.  The resulting circuit is also very robust as it already accounts for possible variations in manufacturing that contribute to varying time delays.  Additionally even in synchronous systems, small asynchronous circuits are needed to match the inputs coming in from different circuits with different clock frequencies or from the outside world.  For large synchronous circuits clock skew from different parts of the system is also an issue and may be solved with asynchronous methods. \\ %Martin did not give references for these....prob ok then

@@

Muller circuits is the approach that D. E. Muller originally proposed based on this delay model \cite{Muller_59}.  Since then a number of synthesis methods following this design has been produced.  Usually the synethsis methods begin with some higher-level specification such as signal transition graph or petri nets and translate into a state graph.  State graphs describes the progression of changes of a finite number of signals.  (The term wires and signals are used interchangeably as the state graph is converted into a circuit.)  Then depending on the underlying implementation, such as generalized C-element and standard C-implementations, the appropriate inputs and logic functions that allows the circuit to function according to the state graph is synthesized.  The end result is a hazard-free and speed independent asynchronous circuit.  We assume that the previous steps are hidden, and are presented with a semi-modular circuit to make fault-tolerant.     
There are other types of delay models and asynchronous circuit synthesis methods such as Quasi Delay Insensitive circuits and the relevant types for this work are described in more detail in the literature review.  \\  %add refs to gen C etc

\section{Organization of this work}
%why are async circuits important, timing delay etc
Because these various faults can interfere with the function of the circuit and even result in harmful operations (catastrophic failures), there has been a lot of work put into making digital circuits fault-tolerant. Most of the fault-tolerant solutions has been investigated for synchronous digital circuits.  Because the timing difference between different signals arriving do not have to be considered for synchronous circuits, they can use error correcting codes and redundancy techniques such as triple modular redundancy (TMR). Unfortunately many of these techniques have problems if directly implemented in asynchronous circuits.\\

In this work, we propose a new fault-tolerant circuit transformation on asynchronous semi-modular control circuits.  We also propose a method of comparing the fault-tolerant circuit with the original circuit, by comparing traces with the half circuit.  The fault free half of the fault-tolerant circuit behaves like the original circuit under single transient faults.  In addition, we assume a gate level model of the circuit and allow the transient to occur on any of the wires thus solving the transient fault problem for a bigger class of circuits than the current state-of-the-art.\\

In the rest of this work, in chapter two, I will first introduce the different types of common faults and their causes, as well as the common fault models that researchers use when investigating these faults.  Then I will go into depth about the asynchronous circuit models that are relevant to this work.  I will then go through the existing body of work on fault-tolerant solutions for both types of circuits with an emphasis on asynchronous circuits.  In chapter three, I will show why the existing fault-tolerant methods are insufficient and propose a new fault free method for asynchronous transient faults.  I will prove using logical proofs as well as formal verification methods to show why my new method always works.  In the final chapter, chapter four, I will conclude on how to better build fault free asynchronous circuits and suggest some possible new research directions.
%Overview:  why is the problem important  \\  maybe I can extend the Introduction a bit more

@@

\subsection{Speed Independent Circuits}
As mentioned in the introduction, circuits are composed of gates and wires.  The unbounded gate delay model assumes an arbitrary delay on all the gates and no delay on wires.  This delay model is the basis for Muller circuits \cite{Muller_59}.  Circuits that operate correctly regardless of the delay are called Speed Independent Circuits.  The correct operation is specified when designing the circuit, for example, given some input values the circuit will return specified output values.  
There are many ways to represent specifications such as petri nets and state graphs, and there are established methods to build asynchronous circuits to satisfy the specifications.  We won't go into these representations and methods in detail, other than the aspects that are relevant to this work.  We consider circuits which has wires that take on Boolean values of either `1' or `0'.\\
%Wires in the circuits take on Boolean values of either `1' or `0'.  A state is defined by assigning a Boolean value to each wire of the circuit.  States are unique in that no two states share the same wire values.  There will be a formal definition of wires and states in the next chapter.

@@

@@

\begin{proof}
Let $\sigma$ be an arbitrary trace of the fault-tolerant circuit.  We will show by induction on $n$ that Lemma 1 is true for any prefix of the trace $\sigma_n$, where $n$ is an integer from 1 to the length of the trace.  
%We will show by induction on $n$ that for any prefix of the trace $\sigma_n$, where $n$ is an integer from 1 to the length of the trace, $h^A(\sigma_n)$ is a prefix of a trace of the original circuit.
% true but needs to find a new home -> either $h^A(s_n)=h^A(s_{n+1})$ or $T(h^A(s_n), h^A(s_{n+1}))$
We show the induction hypothesis holds in the base case of $\sigma_1$ consisting of state $s_1$, a valid initial state by construction.
\begin{itemize}
\item For every $s_1$ that is a valid initial state, we have that $h^A(s_1)$ is some state in the original circuit by construction. %how to compare with OG circuit NEED TO FIX!!
 Thus $h^A(s_1)$ is a prefix of length 1 of a trace in the original circuit and P1 holds.
%\item We assigned the initial wire values so that the logic blocks are in a semi-modularity consistent state so P2 holds.
\item 
For any wire, the valid initial state (definition) assigns wires $c1^A$, $c2^A$, $c3^A$ and $w^A$ the same values.  Therefore only wire $c1^A$ may be excited. Since all output/input wires have the same values in the original and fault-tolerant circuit, if wire $w$ is excited in the original circuit, then $c1^A$ must be excited in the fault-tolerant circuit.  %ANOTHER INSTANCE OF MAY BE USING ANOTHER LEMMA, observation?
If wire $w$ is unexcited in the original circuit, then $c1^A$ is unexcited in the fault-tolerant circuit.  This shows the valid initial state satisfies P2.    %is this enough.... that the existing states follow that iff statement?
\end{itemize}

The induction step is to assume that the induction hypothesis is true for a length $k$ prefix $\sigma_k$ of a given trace.  We will prove that the induction hypothesis is true for $\sigma_{k+1}$ by first proving it for the set of all possible traces of length $k+1$ (including prefix of traces longer than $k+1$) with $\sigma_k$ as their first $k$ terms.  %/length $k$ prefix  
The trace $\sigma_{k+1}$ is an element in this set and consequently the induction hypothesis is true for $\sigma_{k+1}$ as well.  
%We will prove that the induction hypothesis is also true for all $\sigma_{k+1}$ that exist. 
To show the hypothesis is true for all such length $k+1$ traces, it is equivalent to considering all possible transitions from the state $s_k$ and showing the hypothesis is true for the new state $s_{k+1}$ in the fault-tolerant circuit.\\

In fact, the possible transitions can be neatly partitioned into the cases in Figure \ref{fig:l1helper}.  From state $s_k$, we examine all possible transitions that change wire values in the A-half; a transition may occur on excited gates or C-elements.  We ignore transitions in the B-half because those transitions do not change wire values in the A-half and the resulting states are deleted during the half circuit mapping.  In addition, from the induction hypothesis, P1 and P2 are true for the current state $s_k$.   Thus wire blocks in the A-half in state $s_k$ are in one of the cases in Figure \ref{fig:l1helper}, and the transitions in the A-half can only occur in wire blocks that are in cases 1-4 of the figure.  (By P2, if a wire block $w$ 
is excited in state $s_k$, then the corresponding wire $w$ is excited in the original circuit in state $h^A(s_k)$.  To cover all transitions, it suffices to examine transitions in an excited wire block from cases 1-4. ) \\

@@

%P3 states that the wire block must be in a state a-d) of figure \ref{fig:l1helper}.  We consider what happens if a wire transitions from each state. 
%logic gate excited = c1^A excited
%possibly add graph to illustrate this
\begin{figure}
  \centering
    \includegraphics[width=\textwidth]{gatewl2}
  \caption{Different cases of P2 for a wireblock, a-d correspond to excited wire in the original circuit and e is unexcited.  1) case 1, 2) case 2, 3) case 3, 4) case 4, 5) case 5}
  \label{fig:l1helper}
\end{figure}

We prove P1 and P2 sequentially for $s_{k+1}$.  The proof for P1 only relies on the induction hypothesis being true in state $s_k$ and is as follows: \\

\begin{itemize}
We first show that P1 is true for $\sigma_{k+1}$.  
\item We consider transitions from cases 1-3 together (1-3 in Figure \ref{fig:l1helper}). (maybe still need to be more clear about wire block vs transitions) 
If an excited wire block $w$ is in any of these 3 cases, there is only one possible transition for each case: the new value of the signal propagates down the C-element chain.  Thus in the new state $s_{k+1}$, wire block $w$ is in cases 2-4 respectively.  For all 3 cases, the transition occurs on an intermediate wire and $h^A(s_{k+1})=h^A(s_{k})$.  This is a repeated state under the half circuit mapping and is deleted in the resulting trace.  Thus $h^{A}(\sigma_{k+1})=h^{A}(\sigma_k)$ and therefore $h^{A}(\sigma_{k+1})$ must also be a prefix of a trace of the original circuit. 
\item Case 4 is when $w^A$ transitions in the fault-tolerant circuit, as shown in case d of Figure \ref{fig:l1helper}.  Then in the original circuit, the transition from state $h^A(s_k)$ to state $h^A(s_{k+1})$ is on wire $w$.  Because wire $w$ is excited in state $h^A(s_k)$, this is a valid transition (i.e., $T(h^A(s_k), h^A(s_{k+1}))$) and $h^{A}(\sigma_{k+1})$ is a prefix of a trace of the original circuit. 
\end{itemize}

Next, we show that P2 is true for $s_{k+1}$.  Again we consider all possible transitions that lead to the new state $s_{k+1}$.  The wireblock which transitions, which we again name $w$, is in one of cases 1-4.

\begin{itemize}
\item Again, we consider transitions from cases 1-3 together (1-3 in Figure \ref{fig:l1helper}).  We use the following fact from the P1 proof: in the new state $s_{k+1}$, the wireblock $w$ is in cases 2-4 respectively and $h^A(s_{k+1})=h^A(s_{k})$.  Since $h^A(s_{k+1})=h^A(s_{k})$, then all wires in the original circuit do not change excitations in the new state $h^A{s_{k+1}}$.  Then $w$ in the original circuit remains excited in state $h^A{s_{k+1}}$, while wireblock $w$ in the fault tolerant circuit is in one of cases 2-4 in state $s_{k+1}$.  Thus, wireblock $w$ satisfies P2.  All other wireblocks in the fault-tolerant circuit do not change cases in the new state $s_{k+1}$.  (explain why? does it involve `P2')  
Thus all wireblocks of the fault-tolerant circuit in state $s_{k+1}$ satisfy P2, so P2 is true for the trace $\sigma_{k+1}$.

@@

%\begin{figure}
%  \centering
%    \includegraphics[width=\textwidth]{sml1}
%  \caption{An example of wire block $v$ in case 2.  The figure shows wire block $v$ in the fault-tolerant circuit and wire $v$ in the original circuit in states $s_k$ and $s_{k+1}$.  Each arrow denotes a transition}
%  \label{fig:sml1}
%\end{figure}
\item
Wireblock $w$ is a case of its own.  Wire $w$ in the original circuit in state $h^A(s_{k+1})$ has just transitioned and is unexcited since $w$, (this explanation is still a bit weird) the only wire value that changed, is not an input to itself.  In the fault-tolerant circuit, $w^A$ just transitioned and none of the C-element down the chain is excited.  $c1^A$ must remain unexcited since $w$ is unexcited in the original circuit.  Thus wireblock $w$ in state $s_{k+1}$ is in case 5 of Figure \ref{fig:l1helper}.  And as previously mentioned, wire $w$ is unexcited in state $h^A(s_{k+1})$ and thus P2 holds for wire block $w$.

>>>>

\begin{document}
\chapter{Introduction}

Faults in digital circuits arise from sources such as fabrication defects and radiation.  These faults can ultimately lead to failures of the component.  Thus fault tolerant designs are crucial especially in applications where errors can have disastrous consequences such as in aviation or banking.  Moreover, due to new technology and shrinking transistor sizes for MOSFETs, radiation effects become more prominent.  Because designing fault-tolerant circuits is such an important problem, there has been significant previous work done on fault-tolerance for synchronous circuits.  However there are less work done on fault-tolerant asynchronous circuits.  The research described here aims to fill that gap.\\

Asynchronous circuits differ from synchronous circuits in that the gates have arbitrary delays so asynchronous designs must be more meticulous to account for these delays.  The arbitrary delays also make fault-tolerance a harder problem.  For example, the classic solution of Triple Modular Redundancy (TMR) does not work for asynchronous circuits.  The main contribution of this work is proposing a new fault-tolerant design for asynchronous circuits.  The new design expands fault-tolerance to semi-modular speed independent circuits composed of two-input gates and C-elements.  This work also proves that the proposed fault-tolerant design is tolerant to transient faults.  With this new design, circuits can be more robust to different types of errors, allowing the circuits to be used in a greater variety of environments.

%Digital circuits is the basis of many of present day electronics.  Digital circuits has signals which are represented as discrete values.  This is achieved by choosing a range of voltages that correspond to each discrete value.  Many digital circuits use binary values, that is the signals can only take on the value `logic 0' or `logic 1' (or low/high).  One advantage of only allowing discrete values is that digital circuits are much more robust to noise fluctuations in voltage.  Disregarding the lower level implementation, one can also abstract the function of digital circuits in terms of gates.\\

%Although digital circuits are less sensitive to errors due to noise, it can experience other faults in its electronics which ultimately may lead to failure of the component.  Faults may arise due to fabrication defects and radiation such as from space.  Moreover due to new technology and shrinking transistor sizes for MOSFETs, radiation have caused more noticeable effects even at sea level. Thus designing fault free circuits is an important problem to study and solve.  \\  %can still be expanded

%This work focuses on a class of digital circuits known as asynchronous circuits.  There is an arbitrary delay on the gates of asynchronous circuits so that each design must be additionally verified to operate correctly under such delays.  There is a variety of uses of asynchronous circuits because it has speedups over synchronous circuits and is also useful for synchronous systems where there is significant clock skew or combining components with different clock cycles and/or interfacing with the real world.  There are some previous work that has been done to make asynchronous circuits fault-tolerant to soft errors.  The design is based on duplicating the circuit and only works for quasi-delay-insensitive circuits which requires a lot of assumptions about how the delays in the underlying transistors function.  The main contributions of this work are that it extends the previous work by proposing a new design.  The new design also follows the duplication strategy but makes fault-tolerant the class of semi-modular speed independent circuits (a class of circuits about the same size as QDI circuits) with looser assumptions on the delay and without significant overhead.  Namely the only assumption is that the combinational logic components are composed of gates and that each gate is allowed to have arbitrary delay, instead of assuming that there is no delay in these components.  Previous designs do not work for this more generalized case of circuits.  This work also proves that such a fault-tolerant model will always work and correct transient faults.  This allows for circuits to be more robust to different types of errors that may occur and prolong the lifetime and types of environments this circuit can be used for.

\section{Synchronous vs Asynchronous circuits}
Digital circuits can be divided into two types, synchronous and asynchronous.  The time it takes for gates to process input signals and then propagate the output to the next gates in a digital circuit may vary widely.  If the timing is somehow off, it is possible for the outputs to be different from the desired value resulting in incorrect computation. In synchronous systems this timing variation is dealt with by using a global clock.  The clock is then fed into each flip flop so that the flip flop outputs will lock and update the signals synchronously. The clock cycle frequency is chosen so that all of the gates can finish processing and the correct values are locked for the next cycle. That is, the clock cycle is usually designed to accommodate the slowest logic element. The design of synchronous systems can be complex and is not necessary to understand in detail for this work. \\
\begin{figure}
\includegraphics[width=\textwidth]{syncex}
\captionof{figure}{Example of a synchronous digital circuit.  Each output is gated by a flip flop that is controlled by the clock}
\end{figure}
%possible picture of clock and flip flops?.... redraw as my own

Asynchronous circuits, as the name suggests, do not depend on a clock. As a result there are varying time delays in their components. The goal of designing asynchronous circuits is to make circuits that achieve some specification in spite of the time delays. That is, irrespective of the time delays, the circuit meets its specification. One main reason that asynchronous circuits are used is that they do not require clocks to propagate signals; instead as soon as one logic element finishes the signal goes directly to the next element.  This can allow the circuits to have speedups as it is not waiting for the slowest element for each clock cycle.  The resulting circuit is also very robust as it already accounts for possible variations in manufacturing that contribute to varying time delays.  Additionally even in synchronous systems, small asynchronous circuits are needed to match the inputs coming in from different circuits with different clock frequencies or from the outside world.  For large synchronous circuits, clock skew from different parts of the system is also an issue and may be solved with asynchronous methods. \\ %Martin did not give references for these....prob ok then

@@

D. E. Muller proposed essentially this class of speed independent circuits, which are sometimes called Muller circuits \cite{Muller_59}.  Since then a number of synthesis methods following this design has been produced.  Usually the synthesis methods begin with some higher-level specification such as signal transition graph or Petri nets and translate into a state graph.  A state graph describes all the possible sequences of changes in a finite number of signals.  (The term wires and signals are used interchangeably as the state graph is converted into a circuit.)  Then depending on the underlying implementation, such as generalized C-element and standard C-implementations, the appropriate inputs and logic functions that allow the circuit to function according to the state graph is synthesized.  The end result is a hazard-free and speed independent asynchronous circuit.  The construction we describe begins with a semi-modular circuit, possibly resulting from the previously described process, and transforms it into a circuit that can tolerate any single transient fault.

%There are other types of delay models and asynchronous circuit synthesis methods such as Quasi Delay Insensitive circuits and the relevant types for this work are described in more detail in the literature review.  \\  %add refs to gen C etc

\section{Organization of this work}
%why are async circuits important, timing delay etc
Because these various faults can interfere with the function of the circuit and even result in harmful operations (catastrophic failures), there has been a lot of work on making digital circuits fault-tolerant. Most of the fault-tolerant solutions have been investigated for synchronous digital circuits.  Because the timing difference between different signals arriving do not have to be considered for synchronous circuits, they can use error correcting codes and redundancy techniques such as triple modular redundancy (TMR). Unfortunately most of these techniques are not applicable to asynchronous circuits.\\

In this work, we propose a new fault-tolerant circuit transformation on asynchronous semi-modular control circuits.  We also propose a method of comparing the fault-tolerant circuit with the original circuit, by comparing traces with the half circuit.  The fault-free half of the fault-tolerant circuit behaves like the original circuit under single transient faults.  In addition, we assume a gate-level model of the circuit and allow the transient to occur on any of the wires thus solving the transient fault problem for a bigger class of circuits than the current state-of-the-art.\\

The rest of this work is organized as follows.  Chapter two introduces the different types of common faults and their causes, as well as the common fault models that researchers use when investigating these faults.  Also included in chapter two are the asynchronous circuit models that are relevant to this work.  In addition, there is discussion about the existing body of work on fault-tolerant solutions for both types of circuits with an emphasis on asynchronous circuits.  Chapter three provides the background terminology and definitions for asynchronous circuits.  Chapter four shows why the existing fault-tolerant methods are insufficient and propose a new fault-tolerant method for asynchronous transient faults.  We prove the correctness of the method using a combination of automated formal verification and manual methods.  And finally chapter five discusses how to better build fault-tolerant asynchronous circuits and suggests some possible new research directions.
%Overview:  why is the problem important  \\  maybe I can extend the Introduction a bit more

@@

\subsection{Speed Independent Circuits}
As mentioned in the introduction, circuits are composed of gates and wires.  The unbounded gate delay model assumes an arbitrary delay on all the gates and no delay on wires.  This delay model is the basis for Muller circuits \cite{Muller_59}.  Circuits that operate correctly regardless of the delay are called Speed Independent Circuits.  The correct operation is specified when designing the circuit, for example, given some input values the circuit will return specified output values.  
There are many ways to represent specifications such as Petri nets and state graphs, and there are established methods to build asynchronous circuits to satisfy the specifications.  We won't go into these representations and methods in detail, other than the aspects that are relevant to this work.  We consider circuits which has wires that take on Boolean values of either `1' or `0'.\\
%Wires in the circuits take on Boolean values of either `1' or `0'.  A state is defined by assigning a Boolean value to each wire of the circuit.  States are unique in that no two states share the same wire values.  There will be a formal definition of wires and states in the next chapter.

@@

\begin{lemma}[0]
Given two identical logic blocks $f$ and $g$, if the inputs into $f$ and $g$ have the same values then:\\
i)  if the outputs are the same value and $f$ is excited then $g$ is also excited.\\
ii)  if the outputs are the same value and $f$ is unexcited then $g$ is also unexcited.\\
iii)  if the outputs are different values and $f$ is excited then $g$ is unexcited.
\end{lemma}
\begin{proof}
i) \& ii)  Since $f$ and $g$ are identical gates or C-elements then if the inputs and output are the same values, $f$ and $g$ must be both excited or both unexcited. \\

iii)  We prove this by contradiction.  Suppose that inputs to $f$ and $g$ are the same and the outputs are different values and both $f$ and $g$ are excited.  This means that for some circuit element that these input values both cause the element to excite to 1 and 0 at the same time.  This cannot happen in any of the elements that we build our circuit from and is therefore a contradiction.
\end{proof}

%MAPPING PROPERTY?
In the following lemmas and theorems we compare a state $s$ in the fault-tolerant circuit with its mapped state $h^A(s)$ in the original circuit.  Due to the mapping and architecture of the circuits, for any wire block $w$, the inputs to the logic block of $w^A$ in the fault-tolerant circuit has the same value as the inputs to the logic block of $w$ in the original circuit.  This fact is used extensively in combination with Lemma 0.  The excitation on $w$ in the original circuit can sometimes be deduced from semi-modularity, then by applying Lemma 0 we can also derive the excitation on $w^A$.  \\
%compare with original circuit: logic block with same inputs.....if input cause block to be excited... if output is same too then the state of logic block is identical.

@@

\begin{proof}
Let $\sigma$ be an arbitrary trace of the fault-tolerant circuit.  We will show by induction on $n$ that Lemma 1 is true for the length $n$ prefix of the trace $\sigma_n$.  
%We will show by induction on $n$ that for any prefix of the trace $\sigma_n$, where $n$ is an integer from 1 to the length of the trace, $h^A(\sigma_n)$ is a prefix of a trace of the original circuit.
% true but needs to find a new home -> either $h^A(s_n)=h^A(s_{n+1})$ or $T(h^A(s_n), h^A(s_{n+1}))$
We first show the induction hypothesis holds in the base case of $\sigma_1$ consisting of state $s_1$, a valid initial state by construction.
\begin{itemize}
\item State $s_1$ is a valid initial state so $h^A(s_1)$ is a state in the original circuit by construction. %how to compare with OG circuit NEED TO FIX!!
 Thus $h^A(s_1)$ is a prefix of length 1 of a trace in the original circuit and satisfies P1.
%\item We assigned the initial wire values so that the logic blocks are in a semi-modularity consistent state so P2 holds.
\item 
For each wireblock, the valid initial state initializes wires $c1^A$, $c2^A$, $c3^A$ and $w^A$ to the same value.  Therefore only wire $c1^A$ may be excited.  Since the mapping gives identical inputs then by Lemma 0 i) ii) if wire $w$ is excited in the original circuit, $c1^A$ is also excited in the fault-tolerant circuit.
And if wire $w$ is unexcited in the original circuit, then $c1^A$ is unexcited in the fault-tolerant circuit.  This shows that state $s_1$ satisfies P2.    %is this enough.... that the existing states follow that iff statement?
\end{itemize}

The induction step is to assume that the induction hypothesis is true for all length $k$ prefixes of traces of the fault-tolerant circuit.  We will prove that the induction hypothesis is true for all length $k+1$ prefixes.  %/length $k$ prefix  
%We will prove that the induction hypothesis is also true for all $\sigma_{k+1}$ that exist. 
Let $\sigma_k$ be an arbitrary length $k$ prefix and $s_k$ its $k$-th state.  
To show the hypothesis is true for all length $k+1$ prefixes, equivalently we show the hypothesis is true for all possible next states $s_{k+1}$ from the state $s_k$.\\

In fact, the possible next states can be partitioned into transitions from each of the cases in Figure \ref{fig:l1helper}.  To see this, we first note that examining the transitions in only the A-half is sufficient.  Transitions in the B-half can be ignored under the $h^A$ mapping because such transitions do not change wire values in the A-half and the resulting states are deleted by the mapping.  We know by the induction hypothesis that P1 and P2 are true for the current state $s_k$.  In particular, P2 states that all wire blocks in state $s_k$ are in one of the cases in Figure \ref{fig:l1helper}.  Only cases 1-4 have excited gates or C-elements that are capable of a transition.  Thus, to cover all possible transitions, it suffices to examine transitions in an excited wire block from cases 1-4. \\
%(By P2, if a wire block $w$ is excited in state $s_k$, then the corresponding wire $w$ is excited in the original circuit in state $h^A(s_k)$.  To cover all transitions, it suffices to examine transitions in an excited wire block from cases 1-4. )

@@

%P3 states that the wire block must be in a state a-d) of figure \ref{fig:l1helper}.  We consider what happens if a wire transitions from each state. 
%logic gate excited = c1^A excited
%possibly add graph to illustrate this
\begin{figure}
  \centering
    \includegraphics[width=\textwidth]{gatewl2}
  \caption{Different cases of P2 for a wireblock, 1-4 correspond to excited wire in the original circuit and 5 is unexcited.  1) case 1, 2) case 2, 3) case 3, 4) case 4, 5) case 5}
  \label{fig:l1helper}
\end{figure}

We first prove P1 and then P2 for the length $k+1$ prefix.  To show P1 is true for state $s_{k+1}$, we must show that $h^A(s_{k+1})$ is a reachable state and that ($h^A(s_{k})$,$h^A(s_{k+1})$) is a transition in the original circuit.  The proof for P1 relies only on the induction hypothesis being true for state $s_k$ and is as follows: \\

Let the transitioning wire block from state $s_k$ be called $w$.  There are four cases that $w$ can be in.  % A transition occurs on a wire block that is in cases 1-4. 
\begin{itemize}  
\item Cases 1-3 (Figure \ref{fig:l1helper}) are considered together.  
If an excited wire block $w$ is in any of these three cases, there is only one possible transition for each case: the new wire value propagates down the C-element chain.  That is, in state $s_{k+1}$, wire block $w$ is in cases 2-4 respectively.  For all three cases, the transition occurs on an intermediate wire and $h^A(s_{k+1})=h^A(s_{k})$.  This is a repeated state under the half circuit mapping applied to the trace and is deleted.  Thus $h^{A}(\sigma_{k+1})=h^{A}(\sigma_k)$ and $h^{A}(\sigma_{k+1})$ must also be a prefix of a trace of the original circuit. 
\item Case 4 (Figure \ref{fig:l1helper}) has only one possible transition which is on wire $w^A$.  Then under the half circuit mapping, wire $w$ transitions from state $h^A(s_k)$ to state $h^A(s_{k+1})$.  By P2, wire $w$ is also excited in state $h^A(s_k)$ and this is a valid transition (i.e., $T(h^A(s_k), h^A(s_{k+1}))$).  Therefore $h^{A}(\sigma_{k+1})$ is a prefix of a trace of the original circuit. 
\end{itemize}

That concludes the proof for P1.  Next, we show that P2 is true for all possible $s_{k+1}$ by showing that $s_{k+1}$ in the fault-tolerant circuit corresponds to $h^A(s_{k+1})$ in the original circuit with certain properties of the wireblocks preserved.  Again, there are four cases that the transitioning wireblock $w$, can be in.

\begin{itemize}
\item Cases 1-3 (Figure \ref{fig:l1helper}) are considered together.  As mentioned in the P1 proof, the transition occurs on an intermediate wire and $h^A(s_{k+1})=h^A(s_{k})$.  Since $h^A(s_{k+1})=h^A(s_{k})$, then all wires in the original circuit do not change excitations in the new state $h^A(s_{k+1})$.  Then $w$ in the original circuit remains excited in state $h^A(s_{k+1})$, while wireblock $w$ in the fault tolerant circuit is in one of cases 2-4 in state $s_{k+1}$.  Wireblock $w$ satisfies P2.  All other wireblocks in the fault-tolerant circuit do not change cases in the new state $s_{k+1}$.  
Thus all wireblocks of the fault-tolerant circuit in state $s_{k+1}$ satisfy P2.

@@

%\begin{figure}
%  \centering
%    \includegraphics[width=\textwidth]{sml1}
%  \caption{An example of wire block $v$ in case 2.  The figure shows wire block $v$ in the fault-tolerant circuit and wire $v$ in the original circuit in states $s_k$ and $s_{k+1}$.  Each arrow denotes a transition}
%  \label{fig:sml1}
%\end{figure}
\item
Wireblock $w$ is a special case of case 4.  Wire $w$ of the original circuit has just transitioned in state $h^A(s_{k+1})$.  Since $w$, the only wire value that changed, is not an input to itself, $w$ is unexcited in state $h^A(s_{k+1})$.  In the fault-tolerant circuit, $w^A$ just transitioned so the wireblock $w$ is in either case 1 or case 5.  By Lemma 0 ii), since $w$ is unexcited in the original circuit $c1^A$ is also unexcited.  Thus wireblock $w$ in state $s_{k+1}$ is in case 5 while wire $w$ in state $h^A(s_{k+1})$ is unexcited.  Thus P2 holds for wire block $w$ in state $s_{k+1}$.

%By semi-modularity, if a wire is excited in state $h^A(s_{k})$ and does not transition, then it remains excited in state $h^A(s_{k+1})$.  
%Thus, the only wire that is excited in state $h^A(s_{k})$ and unexcited in state $h^A(s_{k+1})$ is the transitioning wire $w$ (since $w$ is not its own input).
%  In state $s_{k+1}$, $w^A$ transitions and since $c1^A=w$, $c1^A$ remains unexcited, so wire block $w$ is in case 5 of Figure \ref{fig:l1helper}.  Thus P3 holds for wire $w$.  
\item
For wireblocks in case 5 in state $s_k$, we show that these wires stay in case 5 or transition to case 1 in state $s_{k+1}$.  Let us call such a wireblock $u$.  By P2, $u$ is unexcited in the original circuit in state $h^A(s_{k})$.  There are two possibilities in the next state: $u$ can be excited or unexcited in state $h^A(s_{k+1})$.  We first note that by the half circuit mapping on $s_{k+1}$, the inputs to $u$ in the original circuit and $c1^A$ of wireblock $u$ in the fault-tolerant circuit have the same values, and also $c1^A=u$.  \\
If $u$ is excited, then by Lemma 0 i) $c1^A$ in the fault-tolerant circuit is also excited in state $s_{k+1}$.  Then wireblock $u$ is in case 1 (Figure \ref{fig:l1helper}) in state $s_{k+1}$.  Thus P2 holds for wires of this type in state $s_{k+1}$.\\
And if $u$ remains unexcited in state $h^A(s_{k+1})$, by Lemma 0 ii) $c1^A$ of wireblock $u$ is unexcited in state $s_{k+1}$.  Then wireblock $u$ stays in case 5 of Figure \ref{fig:l1helper}.  Thus P2 holds for wires of this type.
%$u$ that are unexcited in state $h^A(s_{k})$ and transition to excited in state $h^A(s_{k+1})$, in state $s_{k}$ the wire block $u$ is in case 5 of Figure \ref{fig:l1helper}.  But since wire $u$ in the original circuit is excited in state $h^A(s_{k})$ and $c1^A=u$, then $c1^A$ is also excited in state $s_{k+1}$ and the wire block $u$ is in case 1 of Figure \ref{fig:l1helper}.  Thus P3 holds for wires of this type. 
%\item
%Finally for wires that are unexcited in both $h^A(s_k)$ and $h^A(s_{k+1})$, $c1^A$ is unexcited and the wire block stays in case 5 of Figure \ref{fig:l1helper}.  Thus P3 holds for wires of this type. 
\end{itemize}
We have covered all possible wire cases in the circuit.   
Then P2 is true for any transition from case 4. 
\end{itemize}
So the induction hypothesis holds for all possible $\sigma_{k+1}$ and the induction step is complete. \\
By induction on the length of the trace, the first property shows that $h^{A,B}(\sigma_n)$ is the prefix of a trace from the original circuit for all n.
%do I need to show the opposite?  At every step the previous transitions are possible??  Dunno if true for faults though.... also something about collapsed states can't tell the difference?  Can we just map it to a circuit where everything goes together? <- this needs proving?
